%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.85]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Matteo} % Your first name
\familyname{Ansaldi} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{Via Borgo San Dalmazzo, 6}{12012, Boves (CN), Italy}
\mobile{+39 366 351 6370}
\email{ansaldimatteo@outlook.com}
\extrainfo{www.linkedin.com/in/ansaldi-matteo}

%----------------------------------------------------------------------------------------

\begin{document}


%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2017--2019}{Masters Degree in Computer Engineering}{Politecnico di Torino}{Turin}{\textit{110/110}}{}  % Arguments not required can be left empty
\cventry{2013--2017}{Bachelors Degree in Computer Engineering}{Politecnico di Torino}{Turin}{\textit{92/110}}{}

\section{Masters Thesis}

\cvitem{Title}{\emph{Camera-less context detection in mobile platforms}}
\cvitem{Supervisors}{Professor M. Poncino \& Associate Professor D. Jahier Pagliari}
\cvitem{Description}{
    This thesis studied the potential to use low-powered sensors in mobile devices 
    with a Convolutional Neural Network to help reduce battery usage. I developed an Android app in Java 
    to collect the training and testing data as well as implementing the CNN using Python and PyTorch.
}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Professional Experience}

%\subsection{Vocational}

\cventry{09/2020 -- Present}{Associate Solutions Architect}{\textsc{Amazon Web Services}}{Milan}{}{
    My main role as a Solution Architect in AWS involved working directly with greenfield clients in the 
    retail space. I have presented AWS to multiple large Italian companies, and assisted them in developing 
    new applications on AWS or migrating parts of their infrastructure from on-premises to the cloud.
    \newline{}
    While working with AWS, the first 5 months were dedicated to studying the platform's services. I have 
    used multiple services such as EC2, Lambda, API Gateway, DynamoDB, Redshift, CloudWatch, S3, SNS, Amplify 
    and GraphQL to name a few. 
    During this period I have also developed a number of file hosting services fully on AWS to fill in some missing 
    gaps in the tools we had at the time.
}

%------------------------------------------------

\cventry{05/2019 -- 08/2020}{Programmer}{\textsc{Reply S.p.A}}{Turin}{}{
    Worked and lead on multiple projects for external clients. The majority of the time I worked as 
    an iOS developer and maintainer, developing a number of apps while also managing launches along 
    with my couterparts on Android. I also worked as a backend developer on other projects, mainly 
    creating backends in node.js
\newline{}\newline{}
Detailed projects:
\begin{itemize}
\item \textbf{Beretta Firearms}
\newline
    My work on the Shooting Data project involved learning Objective-C 
    and then taking over the role of primary iOS developer on the app, alongside
    the role as maintainer of a parser for data collection. As maintainer of the parser, I was 
    responsible for 
    interacting directly with the clients, using the Azure IoT Hub, and updating the parser 
    in java.
\item \textbf{Vodafone}
\newline
    For this project, I maintained the main backend in node.js for the Smart@Home Vodafone Platform. 
    This required managing multiple databases for each development environment and general maintenance 
    of the backend for push notifications. The main technologies used were node.js, MySQL, and multiple 
    AWS technologies such as SQS, SNS, ECS, RDS, and so on.
\item \textbf{Fondazione Torino Musei}
\newline
    I took on the role of developing the iOS app and designing the backend with 
    Firebase Cloud Firestore. I also had the opportunity to study and implement some Firestore Cloud 
    Functions to keep the data synchonized.
\item \textbf{Caleffi}
\newline
    I worked as an iOS developer on the project, which required designing multiple API 
    calls to our backend, and to develop an interaction flow between a gateway and iPhone 
    via bluetooth commands.
\end{itemize}}

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{Certifications}

\cvitem{2021}{AWS Certified Developer - Associate}
\cvitem{2020}{AWS Certified Solutions Architect - Associate}
\cvitem{2020}{AWS Certified Cloud Practitioner}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Computer skills}
\subsection{Cloud platforms}
\cvitem{Advanced}{AWS}
\cvitem{Basic}{Microsoft Azure, GCP}

\subsection{Programming Languages and tools}
\cvitem{Advanced}{Objective-C, C, node.js, Git}
\cvitem{Intermediate}{Java, Python, Swift, php, SQL, assembly (8086, MIPS, ARM), Docker}
\cvitem{Basic}{Kotlin}

\subsection{Databases}
\cvitem{Advanced}{Amazon DynamoDB}
\cvitem{Intermediate}{Relational Databases (Oracle, MySQL)}
\cvitem{Basic}{Firebase Realtime database, Amazon Redshift}
%----------------------------------------------------------------------------------------
%	PERSONAL SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Personal Skills}
\cvitem{}{
    I have the ability to learn new programming languages and technologies very quickly. When I was hired 
    to work at Concept Reply, I had never used Xcode, Objective-C nor had I programmed 
    for iOS before. After a week of studying the tools I would be using, I was already developing 
    portions of the app to send into production. Within a few months I was the only iOS developer 
    developing and managing the app, and shortly after that I was asked to maintain and continue developing 
    the data parser written in Java. Meanwhile, I also started to work on other backend projects 
    allowing me to explore different cloud platforms. 
    \newline{}
    I've developed good teamwork and relational skills by working in close contact with 
    other colleagues on various projects, while also presenting or pitching our findings directly 
    to clients to get their feedback on solutions we were delivering.
}


%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitemwithcomment{English}{Mothertongue}{C2}
\cvitemwithcomment{Italian}{Mothertongue}{C2}
\cvitemwithcomment{French}{Basic}{A2}

%----------------------------------------------------------------------------------------
%	LEGAL SECTION
%----------------------------------------------------------------------------------------

\emptysection{}\closesection
\vfill
\begin{center}
\textit{\small 
    I hereby give my consent to the processing of my personal data included in my CV according to the General Data Protection
    Regulation (EU Regulation 2016/679) and Legislative decree no.196 of 30th June 2003.
}
\end{center}

%----------------------------------------------------------------------------------------

\end{document}